Solent region: Test Maps

### 2021-07-15 Solent_Mapping_v2.Rmd
Changed the titles and varibale names for linking to work

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # set this to FALSE if you don't want the code in the final oputput

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$`LSOA code (2011)` #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`Index of Multiple Deprivation (IMD) Rank`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Rank", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # set this to FALSE if you don't want the code in the final output

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
